### 2021-10-05 plos_latex_template.tex
refine rule 8 - Batool

% keeping references:
%   However, conferences can become discriminating spaces, in which members of some specific privileged groups reproduce the systematic inequalities that occur in academia and society \cite{arendDisparityConferenceRegistration2019, timperleyHeMoanaPukepuke2020, gewinWhatScientistsShould2019, brownAbleismAcademiaWhere2018}.

@@

% Rocío: Could start with an introduction (or put somewhere else) that online can easily make conferences more inclusive for many people, but not necessarily for people with disabilities, and that they can be easily left behind unless we actively work on their inclusion. 
Conferences are among the least accessible spaces that people with disabilities may encounter \cite{priceAccessImaginedConstruction2009}.
Importantly, accessibility practices are inclusive not only for people with disabilities but can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general. 
% Liz: I don't think it's actually ironic. maybe surprising or counterintuitive? ast: absolutely! i put importantly at the end to highlight that without opposition

@@

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference a voice and sense of belonging. Embedding inclusion in your communication strategy can only come by design, it shouldn’t be a thoughtless default. In the essense of your communication strategy, you should pritorise and attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team. As you plan the conference, actively reach out and promote the conference to people who have been systematically excluded. Design a promotion plan that reaches communities that are traditionally excluded in scientific meetings. This could be by including representatives from these communities in the organising team.Always  include explicit descriptions of accessibility and other inclusion practices. Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers.

>>>>

% keeping references:
%   However, conferences can become discriminating spaces, in which members of some specific privileged groups reproduce the systematic inequalities that occur in academia and society \cite{arendDisparityConferenceRegistration2019, timperleyHeMoanaPukepuke2020, gewinWhatScientistsShould2019, brownAbleismAcademiaWhere2018}.
% Liz adding reference marks2021meeting

@@

% Rocío: Could start with an introduction (or put somewhere else) that online can easily make conferences more inclusive for many people, but not necessarily for people with disabilities, and that they can be easily left behind unless we actively work on their inclusion. 
% Liz: let me know if you want me to take a shot at this.adding reference marks2021meeting

Conferences are among the least accessible spaces that people with disabilities may encounter \cite{priceAccessImaginedConstruction2009}.
Importantly, accessibility practices are inclusive not only for people with disabilities but can be beneficial to a broad spectrum of people. For instance, having captions is helpful to deaf and hard-of-hearing people, non-native speakers, and everyone in general. 
% Liz: I don't think it's actually ironic. maybe surprising or counterintuitive? ast: absolutely! i put importantly at the end to highlight that without opposition

@@

\section{Express the welcoming spirit in your communication strategy}
\label{rule_communication}
%ast: sara mentioned something that can be good spirit for the communication rule: don't do anything to the outside that you are not doing for your team. it's communication strategy but also there should be coherence between your actions and your words. %Rocío: I love that. Please add it.
An inclusive communication is to give each individual within the conference a voice and sense of belonging. Embedding inclusion in your communication strategy can only come by design, it should not be a thoughtless default. In the essence of your communication strategy, there should be coherence between actions and words. Always attend to the needs of your team, in other words, don't do anything to the outside that you are not doing for your team. As you plan the conference, actively reach out and promote the conference to people who have been systematically excluded. Design a promotion plan that reaches communities that are traditionally excluded in scientific meetings. This could be by including representatives from these communities in the organizing team. Always include explicit descriptions of accessibility and other inclusion practices. Help people answer the question "Can I attend this conference?" without the emotional labor of contacting the organizers. Express this welcoming spirit in your communication strategy: Be public about your commitment to equity and inclusion: display the CoC prominently in conference spaces, publish the diversity statement, fee waivers, abstract selection process. Be careful with the language you use in promoting to the conference and how you talk about minoritized people, Assertively set tone of inclusion.
